\mytitle

### 2016-07-29 pdocs/thesis/article-section-3.tex
article-section-3 continues

\section{Processing plasticity}

@@

System has only one dynamic rigid body which is three meters high block of 0.04 \% steel enforced concrete. 
Cross section is one square meter.
Concrete density is $2000 \frac{kg}{m^3}$ and steel density id $7800 \frac{kg}{m^3}$. 
Steel is assumed to handle load in elastic-plastic case. Yield stress of steel is 200 MPa.
Gravity is $10 \frac{m}{s^2}$. Simulation step is $\frac{1}{60} s$ and 10 
iterations are done for single step.

@@

Method btSequentialImpulseConstraintSolver::solveGroupCacheFriendlySetup
in \bullet\ was used to pick up values. Actual values for fixed constraint are shown in table
\ref{tab:fixedBlockValues} and values for elastic-plastic case are shown in tables \ref{tab:epBlockValues} and 
 \ref{tab:ep2BlockValues}. There are currently two alternative six-dof-spring constraint implementations in \bullet\ and 
in this work elastic-plastic versions of both of them were developed. 
Constraint activation of older spring and fixed constraints is implemented so that 
it can be activated explicitly at start of simulation or it can be automatically activated when constraint is violated.
In this case constraint is not activated explicitly and thus block drops freely during first simulation step.

\begin{description}
\item[velError] is calculated using velocities and external impulses of connected bodies. 
 In this case, it is dominant contributor for constraint's impulse.
\item[posError] is calculated by constraint. It is significant factor in designing stable constraints.
 \begin{description}
 \item[In fixed case,] value is about 12 times actual position error. Factor 12 is based on time step (60) 
 and default value of error reduction parameter (0.2).
 \item[In elastic plastic case,]  value is set to zero if impulse would be larger than maximum impulse or
spring simulation cannot be done in stable way.
 \end{description}
\item[rhs] is calculated by velError jInv + posError jInv
\item[jInv] is calculated using masses and constraint geometry. In this case, it is mass of body (6000).
\end{description}

>>>>

% !TeX root = article.tex
\section{Processing plasticity}

@@

\begin{figure}[htb!]
\centering
\begin{tikzpicture}
\coordinate (O) at (0,0,0);

% axes
\draw[->] (O) -- (1,0,0) node[anchor=north east]{$x$};
\draw[->] (O) -- (0,1,0) node[anchor=north west]{$y$};
\draw[->] (O) -- (0,0,1) node[anchor=south]{$z$};

% 1,3,1 block, base at y=1.5
\draw (1,1.5,0) -- ++(0,3,0) -- ++(-1,0,0);
\draw (0,1.5,1) -- ++(1,0,0) -- ++(0,3,0) -- ++(-1,0,0) -- ++(0,-3,0);
\draw (1,1.5,0) -- ++(0,0,1);
\draw (0,4.5,0) -- ++(0,0,1);
\draw (1,4.5,0) -- ++(0,0,1);

\draw[->] (0.5,3,0.5) -- ++(0,1.5,0);
\end{tikzpicture}
\caption{Single body model for plasticy processing demonstration.}
\label{fig:tensionModel}
\end{figure}

System has only one dynamic rigid body which is three meters high block of 0.04 \% steel enforced concrete. 
Cross section is one square meter.
Constraint is set so that connecting frame is at top of block. 
In this case frame could be anywhere but if multiple bodies are involved, connecting frame must be defined
so that it reflects wanted scenario.
Concrete density is $2000 \frac{kg}{m^3}$ and steel density id $7800 \frac{kg}{m^3}$. 
Steel is assumed to handle load in elastic-plastic case. Yield stress of steel is 200 MPa.
Gravity is $10 \frac{m}{s^2}$. Simulation step is $\frac{1}{60} s$ and 10 
iterations are done for single step.

@@

Method btSequentialImpulseConstraintSolver::solveGroupCacheFriendlySetup
in \bullet\ was used to pick up values. Actual values for fixed constraint are shown in table
\ref{tab:fixedBlockValues} and values for elastic-plastic case are shown in tables \ref{tab:epBlockValues} and 
 \ref{tab:ep2BlockValues}. There are currently two alternative six-dof-spring constraint implementations in \bullet\ and 
in this work elastic-plastic versions of both of them were developed. 
Constraint activation of older spring and fixed constraints is implemented so that 
they are activated after constraint is violated.
Thus body drops freely during first simulation step and 
gains enough kinetic energy so that higher impulses are needed in few following steps.

\begin{description}
\item[velError] is calculated using velocities and external impulses of connected bodies. 
 In this case, it is dominant contributor for constraint's impulse.
\item[posError] is calculated by constraint. It is significant factor in designing stable constraints.
 \begin{description}
 \item[In fixed case,] value is about 12 times actual position error. Factor 12 is based on time step (60) 
 and default value of error reduction parameter (0.2).
 \item[In elastic plastic case,]  value is set to zero if impulse would be larger than maximum impulse or
spring simulation cannot be done in stable way.
 \end{description}
\item[rhs] is calculated by velError jInv + posError jInv
\item[jInv] is calculated using masses and inertias of connected bodies and constraint geometry. 
In this case, it is mass of body (6000).
\end{description}
